Quantifying uncertainty in Pareto estimates of global lake area

### 2023-02-06 manuscript/manuscript.tex
figure link fix

For evaluation purposes, I generated a simulated dataset of 153,000 lake areas following the Pareto distribution using inverse transform sampling \citep{newman_power_2005}. Lakes in my simulated dataset have a minimum and maximum area of approximately 0.1 and 81,000 $km^2$ respectively. This maximum was chosen to be approximately as large as Lake Superior but less than the Caspian Sea following \citep{lehnerDevelopmentValidationGlobal2004}. The number of lakes in the simulated dataset was adjusted so that the total “true” area of the dataset (3.28 mil $km^2$) would approximately match (but still exceed) the total reported in the HydroLAKES dataset (2.93 mil $km^2$). I simulated a censored lake dataset by excluding approximately 60\% of lakes in the total dataset. I approximated the "true" lake area total by constructing the empirical distribution function (edf) of the data which approximates the underlying Pareto cdf \citep{newman_power_2005}. Then I used this estimate of the cdf slope to generate cdf estimates for the censored lakes. I combined these cdf estimates with the edf values from the known lakes before calculating the sum of the inverted distribution \ref{fig:predict_area}.

>>>>

For evaluation purposes, I generated a simulated dataset of 153,000 lake areas following the Pareto distribution using inverse transform sampling \citep{newman_power_2005}. Lakes in my simulated dataset have a minimum and maximum area of approximately 0.1 and 81,000 $km^2$ respectively. This maximum was chosen to be approximately as large as Lake Superior but less than the Caspian Sea following \citep{lehnerDevelopmentValidationGlobal2004}. The number of lakes in the simulated dataset was adjusted so that the total “true” area of the dataset (3.28 mil $km^2$) would approximately match (but still exceed) the total reported in the HydroLAKES dataset (2.93 mil $km^2$). I simulated a censored lake dataset by excluding approximately 60\% of lakes in the total dataset. I approximated the "true" lake area total by constructing the empirical distribution function (edf) of the data which approximates the underlying Pareto cdf \citep{newman_power_2005}. Then I used this estimate of the cdf slope to generate cdf estimates for the censored lakes. I combined these cdf estimates with the edf values from the known lakes before calculating the sum of the inverted distribution \ref{fig:predict_censor}.
